DeconvOptim.jl - Signal Deconvolution with Julia

### 2022-08-11 paper/paper.tex
Remove additional file so that paper.tex compiles again
Incoporate review to paper [skip ci]

\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
\usepackage{siunitx}
\usepackage{here}
\newcommand\todo[1]{\textcolor{red}{\textbf{TODO: #1}}}
\begin{document}

@@

\section{Efficient Convolutions}
The mathematical definition of a convolution is
\begin{equation}
    (h * S)(\mathbf r) = \int_{-\infty}^{\infty} h(\mathbf r - \mathbf x) \cdot S(\mathbf x) \, \mathrm d \mathbf x.
    \label{eq:conv}
\end{equation}
To obtain efficient deconvolution algorithms we also need a efficient way to calculate the convolution operations.
Today, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently in real space.
However, often the blurring kernel $h$ is not spatially small and might be also multi-dimensional. In that case, FFT based convolutions
outperform sliding kernels. In microscopy and astronomy that is often the case, since a defocus broadens the PSF.

@@

\section{Experiments}
    In this section we show some experiments and compare parts of the software to other solutions.
    All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.1.
    If possible, all threads were used.
    As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
    Our experiments additionally made use of the following packages in Julia 1.6.2: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
    BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}, FFTW.jl\cite{FFTW05}, LLVM.jl\cite{LLVM.jl-2017}, Optim.jl\cite{mogensen2018optim}
    and  Zygote.jl\cite{Zygote.jl-2018}. 
    \subsection{One-Dimensional Time Series}
        First, we want to demonstrate the deconvolution of an artificial one dimensional dataset blurred with a certain PSF.
        Additionally, we want to demonstrate the mechanism to reduce wrap-around artifacts in the deconvolution.
        On the left hand side in \autoref{fig:1D_dataset} we can see a data series which has been simulated 
        as a convolution with a PSF and degradation with additive Gaussian noise.
        \begin{figure}[H]
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/1d_plot_data_blurred.pdf}
                \caption{}
                \label{fig:1D_dataseta}
            \end{subfigure}%
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/1d_plot_data_res_pad_vs_nopad.pdf}
                \caption{}
                \label{fig:1D_datasetb}
            \end{subfigure}
            \caption{1D data which has been convolved with a PSF and was degraded with additive Gaussian noise with $\sigma=1.0$. Note that for the deconvolution we have chosen a position interval which is well within the full series so that there are not wrap-around artifacts in the measurement.}
            \label{fig:1D_dataset}
        \end{figure}
        On the right hand we can see the results of the following deconvolution:
        \begin{lstlisting}[language=Julia]
r_p, o = deconvolution(measured, psf, loss=Gauss(),
     iterations=12, regularizer=TV(num_dims=1),
     λ=0.05, padding=1)
r, o = deconvolution(measured, psf, loss=Gauss(), 
     iterations=12, regularizer=TV(num_dims=1),
     λ=0.05, padding=0)
        \end{lstlisting}
    The first statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not show these intense spikes at the boundaries as the green curve shows.
    Also we notice that the deconvolved data in \autoref{fig:1D_datasetb} does not show all the details which are visible in the ground truth.
    The reason is that the PSF is a low pass filter and therefore only frequencies which have been passed through the filter 
    can be enhanced in terms of contrast in a deconvolved result.

    \subsection{Influence of Regularizer}
        In this part we want to demonstrate the influence of the regularizer.
        \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurring by a PSF.
        \begin{figure}[h]
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_blurry.png}
                \caption{Measured with Poisson noise}
                \label{fig:fabioa}
            \end{subfigure}%
            \hfill
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
                \caption{Without regularizer $N=50$}
                \label{fig:fabiob}
            \end{subfigure}%
            \hfill
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
                \caption{Without regularizer $N=10$}
                \label{fig:fabioc}
            \end{subfigure}%            
            \hfill
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=0.75\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
                \caption{With regularizer $N=24$.}
                \label{fig:fabiod}
            \end{subfigure}%            
            \caption{a) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
                        Deconvolved b) for 50 iterations without a regularizer c) for 10 iterations without a regularizer d) with Good's roughness regularizer and 
                            converged after 24 iterations with $\lambda=0.03$.}
            \label{fig:image}
        \end{figure}

@@

        \autoref{fig:fabioc} shows the result after 50 iterations of the deconvolution. 
        We see that the image is heavily affected by some artifacts which usually occur after too many iterations without a regularizer.

@@

    \subsection{Multi-Dimensional Microscopy Data}
        To more completely demonstrate the features available in \verb|DeconvOptim.jl|,
        we deconvolve a four dimensional dataset where the measured volume consists of a 3D datasets
        with three different color channels, shown in \autoref{fig:result_3d}.
        Here we assumed a common single 3D PSF for all color channels.
        Julia's broadcast mechanism is able to understand that 
        the data has more dimensions that the PSF and expands the PSF so that a multiplication still works.
        \begin{figure}[h]
            \begin{subfigure}{.25\textwidth}
                \centering
                \includegraphics[width = .85\textwidth]{figures/raw_rgb.png}
            \end{subfigure}%
            \begin{subfigure}{.25\textwidth}
                \centering
                \includegraphics[width = .85\textwidth]{figures/deconvolved_rgb.png}
            \end{subfigure}
            \caption{Slice of a 3D dataset with three different colors. a) is the raw data and b) is the
                    deconvolved image.}
            \label{fig:result_3d}
        \end{figure} 
        We only need to specify for the FFT over which dimensions the convolution should happen.
        Clearly we can see that the deconvolution removed a lot of the background blur.

    \subsection{Performance Comparison}
        Since Julia is often advertised with great performance we compare parts and the full deconvolution to other implementations in
        terms of their total performance.
        \subsubsection{Regularizer}
            In \autoref{tab:reg} we can see the runtimes for different TV regularizer implementations. As we can see, \verb|Tullio.jl| outperforms a plain 
            Julia implementation by more than order of magnitude. Partially, that is caused by \verb|Tullio.jl|
            being able to 
            use of all threads whereas Julia's built in broadcast mechanism is not multi threaded.
            By \textit{plain Julia} we are referring to an implementation which is written with standard Julia Base functions.
            The same plain Julia implementation was then used together with \verb|CUDA.jl|
            to make use of the GPU capabilities. We see that there is a minor benefit in using a GPU for the regularizer instead of 
            the \verb|Tullio.jl| version on the CPU. Unfortunately, GPU support by \verb|Tullio.jl| is still experimental and especially on the gradient step 
            we could not achieve reasonable results with it.
            \begin{table}[h]
                \begin{tabular}{l l l l l}
                    & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
                \hline
                CPU & \SI{83.9}{\milli\second} & \SI{7180}{\milli\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12530}{\milli\second} \\
                \hline
                \hline
                    & JAX & $\nabla$ JAX && \\
                \hline
                CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
                GPU & \SI{0.887}{\milli\second}   & \SI{10.2}{\milli\second}&   &
                \end{tabular}
                \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. 
                    We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
                \label{tab:reg}
            \end{table}
            We also compare the performance to an implementation written in Python with the Framework JAX \cite{jax2018github}. 
            The GPU version seems to outperform the Julia version by roughly a factor of $2 - 3$ in both forward and gradient pass.
            However, on the CPU \verb|Tullio.jl| is considerably faster. 
            In general one could always squeeze more performance out of the gradient calculations if the kernels would be hand optimized.
            In our package we especially try avoid that because of the multi-dimensionality it is much more convenient
            to rely on AD and as shown above the performance is usually acceptable.

@@

        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer 
        and a quadratic non-negativity constraint.
        When the TV regularizer was added the weight was $\lambda = 0.001$.
        The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
        \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU. 
        In the table we show the results of an 
        iterative Richardson-Lucy deconvolution. The regularizer weight was $\lambda=0.001$.\\
        In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
        and the runtime of straightforward Richardson-Lucy deconvolution without a regularizer.\\
        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data, the regularizer weight was $\lambda=10^{-7}$. 
        Since it is hard to judge the quality of those results with a numerical loss function value, 
        we compare them by the NCC, see \autoref{img:results}.
        The CPU versions were multi threaded (if possible). 
        \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
        \todo{anscombe norm speed}
        \todo{Fix table }
        \begin{table}[h]
            \begin{tabular}{l l l}
                & Loss & iterations \\ 
            \hline
            \verb|DeconvOptim.jl| & Poisson & 45 \\
            \verb|DeconvOptim.jl| TV & Poisson & 45\\
            Richardson-Lucy & Poisson & 300 \\
            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 300\\
            \verb|GenericDeconv|  & Poisson & 45\\
            \verb|GenericDeconv| TV & Poisson & 45 \\
            \verb|Huygens| & & \\
            \verb|DeconvolutionLab2| LR & Poisson & 300\\
            \end{tabular}
            \caption{Overview which loss function (noise model) and number of iterations are used.}
            \label{tab:deconvprop}
        \end{table}
        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the GPU
        it was the fastest of the tested packages. 
        We also see that our routine was faster than a plain Richardson-Lucy mainly due to the much lower number
        of iterations.
        On the CPU \verb|DeconvOptim.jl| is only beaten by the commercial \verb|Huygens| software. 
        Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
        \verb|DeconvolutionLab2| is written in Java and also uses hand written gradients but still its speed is poor in
        comparison to all other packages.

@@

\section{Summary}
    In conclusion, \verb|DeconvOptim.jl| is a very performant, flexible deconvolution software to deconvolve multi-dimensional datasets.
    Its focus has been from the beginning to be fast and the source code should be automatic differentiated by the available
    packages in Julia. Usually we would expect that AD decreases performances but still our software is faster than
    many other packages which have been written with hand-optimized gradients.
    Furthermore, our toolbox is not restricted in dimensionality and has mechanism to prevent wrap-around artifacts which
    occur with FFT based convolutions.
    Julia's metaprogramming capabilities together with \verb|Tullio.jl| allow to generate regularizer which have high performance
    and are easy to adapt.
    In future, we want to support more regularizers on GPUs since they can not be handled efficiently with the current \verb|Tullio.jl| solution.
    Also we plan to extend the package to deconvolution of spatially varying kernels which are of importance in optical systems
    with large field of view or poor manufacturing quality.

\section{Acknowledgement}
    This work was partially funded by the Honours Programme of the Friedrich Schiller 
    University of Jena\footnote{\url{https://www.uni-jena.de/en/honours_programme}}.
    We want to thank Michael Abbott because he had the
    initial idea for the metaprogramming regularizers based on \verb|Tullio.jl|. 
    Additionally, we want to thank Scientific Volume Imaging for providing a trial license for Huygens and especially Mark Koenis for advising
    us how to adjust the settings to get optimal performance.

\input{bib.tex}

>>>>

\usepackage{caption}
\usepackage{subcaption}
\usepackage{amsmath}
\usepackage{tikz}
\usepackage{pgfplots}
% \pgfplotsset{compat=1.17}
\usepackage{siunitx}
\usepackage{here}
\newcommand\todo[1]{\textcolor{red}{\textbf{TODO: #1}}}
\begin{document}

@@

\section{Efficient Convolutions}
The mathematical definition of a convolution is
\begin{equation}
    (h * S)(\mathbf r) = \int_{-\infty}^{\infty} h(\mathbf r - \mathbf x) \cdot S(\mathbf x) \, \mathrm d \mathbf x.
    \label{eq:conv}
\end{equation}
To obtain efficient deconvolution algorithms we also need an efficient way to calculate the convolution operations.
Today, convolution operations of spatially small kernels $h$ can be calculated on GPUs very efficiently in real space.
However, often the blurring kernel $h$ is not spatially small and might be also multi-dimensional. In that case, FFT based convolutions
outperform sliding kernels. In microscopy and astronomy that is often the case, since a defocus broadens the PSF.

@@

\section{Experiments}
    In this section we show some experiments and compare parts of the software to other solutions.
All experiments were executed on Ubuntu 20.04 using a AMD Ryzen 5 5600X 6-Core processor (12 threads) with \SI{32}{GB} DDR4 RAM and Julia 1.6.2.
    If possible, all threads were used.
    As GPU accelerator we used a GeForce RTX 2060 SUPER with \SI{8}{GB} memory and CUDA 11.3 and CUDA.jl 3.3.1.
    Our experiments additionally made use of the following packages in Julia 1.6.2: ArrayInterface.jl\cite{DifferentialEquations.jl-2017}, 
    BenchmarkTools.jl\cite{BenchmarkTools.jl-2016}, FFTW.jl\cite{FFTW05}, LLVM.jl\cite{LLVM.jl-2017}, Optim.jl\cite{mogensen2018optim}
    and  Zygote.jl\cite{Zygote.jl-2018}. 
    \subsection{One-Dimensional Time Series}
        First, we want to demonstrate the deconvolution of an artificial one dimensional dataset blurred with a certain PSF.
        Additionally, we want to demonstrate the mechanism to reduce wrap-around artifacts in the deconvolution.
        On the left hand side in \autoref{fig:1D_dataset} we can see a data series which has been simulated 
        as a convolution with a PSF and degradation with additive Gaussian noise.
        \begin{figure}[H]
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/1d_plot_data_blurred.pdf}
                \caption{}
                \label{fig:1D_dataseta}
            \end{subfigure}%
            \begin{subfigure}[b]{.25\textwidth}
                \centering
                \includegraphics[width=\textwidth]{figures/1d_plot_data_res_pad_vs_nopad.pdf}
                \caption{}
                \label{fig:1D_datasetb}
            \end{subfigure}
            \caption{1D data which has been convolved with a PSF and was degraded with additive Gaussian noise with $\sigma=1.0$. Note that for the deconvolution we have chosen a position interval which is well within the full series so that there are not wrap-around artifacts in the measurement.}
            \label{fig:1D_dataset}
        \end{figure}
        On the right hand we can see the results of the following deconvolution.
    The first statement applies a total padding of $1$ meaning that the size is doubled and therefore the measured data is padded.
    As we can see, the blue curve in \autoref{fig:1D_datasetb} does not show these intense spikes at the boundaries as the green curve shows.
        \begin{lstlisting}[language=Julia]
r_p, o = deconvolution(measured, psf, loss=Gauss(),
     iterations=12, regularizer=TV(num_dims=1),
     λ=0.05, padding=1)
r, o = deconvolution(measured, psf, loss=Gauss(), 
     iterations=12, regularizer=TV(num_dims=1),
     λ=0.05, padding=0)
        \end{lstlisting}
    Also we notice that the deconvolved data in \autoref{fig:1D_datasetb} does not show all the details which are visible in the ground truth.
    The reason is that the PSF is a low pass filter and therefore only frequencies which have been passed through the filter 
    can be enhanced in terms of contrast in a deconvolved result.

    \subsection{Influence of Regularizer}
        In this part we want to demonstrate the influence of the regularizer.
        \autoref{fig:fabioa} is a simulated imaged which has been affected by Poisson shot noise and blurring by a PSF.
        \begin{figure}[h]
            \begin{subfigure}[b]{.16\textwidth}
                \centering
                \includegraphics[width=0.99\textwidth]{figures/resolution_test_512.png}
                %\caption{Ground truth.}
                \caption{}
                \label{fig:gt}
            \end{subfigure}%
            \begin{subfigure}[b]{.16\textwidth}
                \centering
                \includegraphics[width=.99\textwidth]{figures/resolution_test_chart_blurry.png}
                %\caption{Measured with Poisson noise}
                \caption{}
                \label{fig:fabioa}
            \end{subfigure}%
            \begin{subfigure}[b]{.16\textwidth}
                \centering
                \includegraphics[width=.99\textwidth]{figures/resolution_test_chart_no_reg_iter_50.png}
                %\caption{Without regularizer $N=50$}
                \caption{}
                \label{fig:fabiob}
            \end{subfigure}%
            \hfill
            \begin{subfigure}[b]{.16\textwidth}
                \centering
                \includegraphics[width=0.99\textwidth]{figures/resolution_test_chart_no_reg_iter_10.png}
                %\caption{Without regularizer $N=10$}
                \caption{}
                \label{fig:fabioc}
            \end{subfigure}%            
            \begin{subfigure}[b]{.16\textwidth}
                \centering
                \includegraphics[width=0.99\textwidth]{figures/resolution_test_chart_regularizer_008_iter_21.png}
                %\caption{With regularizer $N=24$.}
                \caption{}
                \label{fig:fabiod}
            \end{subfigure}%            
            \caption{a) is the ground truth image. b) has been convolved with a PSF and affected by Poisson shot noise (100 photons expected for the brightest pixel). 
            c) is deconvolved for 50 iterations without a regularizer, d) for 10 iterations without a regularizer. e) converged with Good's roughness regularizer and 
                            after 24 iterations with $\lambda=0.03$.}
            \label{fig:image}
        \end{figure}

@@

        \autoref{fig:fabiob} shows the result after 50 iterations of the deconvolution. 
        We see that the image is heavily affected by some artifacts (the dotted patterns) which usually occur after too many iterations without a regularizer.

@@

    \subsection{Multi-Dimensional Microscopy Data}
        To more completely demonstrate the features available in \verb|DeconvOptim.jl|,
        we deconvolve a four dimensional (three spatial dimensions and a color dimension) dataset where the measured volume consists of a 3D datasets
        with three different color channels, shown in \autoref{fig:result_3d}.
        Here we assumed a common single 3D PSF for all color channels.
        Julia's broadcast mechanism is able to understand that 
        the data has more dimensions that the PSF and expands the PSF so that a multiplication still works.
        \begin{figure}[h]
            \begin{subfigure}{.25\textwidth}
                \centering
                \includegraphics[width = .85\textwidth]{figures/raw_rgb.png}
            \end{subfigure}%
            \begin{subfigure}{.25\textwidth}
                \centering
                \includegraphics[width = .85\textwidth]{figures/deconvolved_rgb.png}
            \end{subfigure}
            \caption{Slice of a 3D dataset with three different colors. a) is the raw data and b) is the
                    deconvolved image.}
            \label{fig:result_3d}
        \end{figure} 
        We only need to specify for the FFT over which dimensions the convolution should happen.
        Clearly we can see that the deconvolution removed a lot of the background blur.

    \subsection{Performance Comparison}
        Since Julia is often advertised with great performance we compare parts and the full deconvolution to other implementations in
        terms of their total performance.
        \subsubsection{Regularizer}
            In \autoref{tab:reg} we can see the runtimes for different TV regularizer implementations. As we can see, \verb|Tullio.jl| outperforms a plain 
            Julia implementation by more than order of magnitude. Partially, that is caused by \verb|Tullio.jl|
            being able to 
            use of threads whereas Julia's built in broadcast mechanism is not multi threaded.
            By \textit{plain Julia} we are referring to an implementation which is written with standard Julia Base functions.
            The same plain Julia implementation was then used together with \verb|CUDA.jl|
            to make use of the GPU capabilities. We see that there is a minor benefit in using a GPU for the regularizer instead of 
            the \verb|Tullio.jl| version on the CPU. Unfortunately, GPU support by \verb|Tullio.jl| is still experimental and especially on the gradient step 
            we could not achieve reasonable results with it.
            \begin{table}[h]
                \begin{tabular}{l l l l l}
                    & plain & $\nabla$ plain & \verb|Tullio.jl| & $\nabla$ \verb|Tullio.jl| \\
                \hline
                CPU & \SI{83.9}{\milli\second} & \SI{7180}{\milli\second} & \SI{5.53}{\milli\second}  & \SI{119.8}{\milli\second}   \\ 
                GPU & \SI{2.5}{\milli\second}  & \SI{22.9}{\milli\second}& \SI{4.00}{\milli\second}  & \SI{12530}{\milli\second} \\
                \hline
                \hline
                    & JAX & $\nabla$ JAX && \\
                \hline
                CPU & \SI{48}{\milli\second}   & \SI{364}{\milli\second}&   & \\
                GPU & \SI{0.887}{\milli\second}   & \SI{10.2}{\milli\second}&   &
                \end{tabular}
                \caption{Runtimes of a single Total Variation regularizer calculation for different Julia versions and JAX. $\nabla$ indicates the gradient calculation. 
                    We used a 3 dimensional Float32 array with size $300 \times 300 \times 300$.  }
                \label{tab:reg}
            \end{table}
            We also compare the performance to an implementation written in Python with the Framework JAX \cite{jax2018github}. 
            The GPU version seems to outperform the Julia version by roughly a factor of $2 - 3$ in both forward and gradient pass.
            However, on the CPU \verb|Tullio.jl| is considerably faster. 
            In general one could always squeeze more performance out of the gradient calculations if the kernels would be hand optimized.
            In our package we especially try avoid that because of the multi-dimensionality it is much more convenient
            to rely on AD and as shown above the performance is usually acceptable.

@@

        For the results of \verb|GenericDeconv| (written in Matlab by Rainer Heintzmann) we used a Poisson loss function with a L-BFGS minimizer 
        and a quadratic non-negativity constraint.
        When the TV regularizer was added the weight was $\lambda = 0.001$.
        The general idea of \verb|GenericDeconv| is very similar to \verb|DeconvOptim.jl|.
        \verb|DeconvolutionLab2| offers a wide variety of different algorithms which however only run on a CPU. 
        In the table we show the results of an 
        iterative Richardson-Lucy deconvolution. The regularizer weight was $\lambda=0.001$.\\
        In \verb|DeconvOptim.jl| we measured the runtime of the default deconvolution routine with a Poisson loss function
        and the runtime of straightforward Richardson-Lucy deconvolution without a regularizer.\\
        \verb|ThreeDeconv.jl| is another Julia deconvolution toolbox for deconvolution of three dimensional data, the regularizer weight was $\lambda=10^{-7}$. 
        Since it is hard to judge the quality of those results with a numerical loss function value, 
        we compare them by the NCC, see \autoref{img:results}.
        The CPU versions were multi threaded (if possible). 
        \verb|DeconvolutionLab2|, \verb|Huygens| and \verb|GenericDeconv| were tested under Windows 10 and not Ubuntu.
        \begin{table}[h]
            \begin{tabular}{l l l}
                & Loss & iterations \\ 
            \hline
            \verb|DeconvOptim.jl| & Poisson & 45 \\
            \verb|DeconvOptim.jl| TV & Poisson & 45\\
            Richardson-Lucy & Poisson & 300 \\
            \verb|ThreeDeconv.jl|  & Gauss+Poisson& 300\\
            \verb|GenericDeconv|  & Poisson & 45\\
            \verb|GenericDeconv| TV & Poisson & 45 \\
            \verb|Huygens| & Poisson & 25\\
            \verb|DeconvolutionLab2| LR & Poisson & 300\\
            \end{tabular}
            \caption{Overview which loss function (noise model) and number of iterations are used.}
            \label{tab:deconvprop}
        \end{table}
        As summary of those performance tests we can state that our Julia implementation is very competitive and especially on the GPU
        it was the fastest of the tested packages. 
        We also see that our routine was faster than a plain Richardson-Lucy mainly due to the much lower number
        of iterations.
        On the CPU \verb|DeconvOptim.jl| is only beaten by the commercial \verb|Huygens| software. 
        Despite \verb|ThreeDeconv.jl| written in Julia it is notably slower in comparison to our implementation.
        \verb|DeconvolutionLab2| is written in Java and also uses hand written gradients but still its speed is poor in
        comparison to all other packages.

@@

\section{Summary}
    In conclusion, \verb|DeconvOptim.jl| is a very performant, flexible deconvolution software to deconvolve multi-dimensional datasets.
    Its focus has been from the beginning to be fast and the source code should be automatic differentiated by the available
    packages in Julia. Usually we would expect that AD decreases performances but still our software is faster than
    many other packages which have been written with hand-optimized gradients.
    Furthermore, our toolbox is not restricted in dimensionality and has mechanism to prevent wrap-around artifacts which
    occur with FFT based convolutions.
    Julia's metaprogramming capabilities together with \verb|Tullio.jl| allow to generate regularizers which have high performance
    and are easy to adapt.
    In future, we want to support more regularizers on GPUs since they can not be handled efficiently with the current \verb|Tullio.jl| solution.
    Also we plan to extend the package to deconvolution of spatially varying kernels which are of importance in optical systems
    with large field of view or poor manufacturing quality.

\section{Acknowledgement}
    This work was partially funded by the Honours Programme of the Friedrich Schiller 
    University of Jena\footnote{\url{https://www.uni-jena.de/en/honours_programme}}.
    We want to thank Michael Abbott because he had the
    initial idea for the metaprogramming regularizers based on \verb|Tullio.jl|. 
    Additionally, we want to thank Scientific Volume Imaging for providing a trial license for Huygens and especially Mark Koenis for advising
    us how to adjust the settings to get optimal performance. 
\newpage
\input{bib.tex}
